%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1.1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://linkedin.com/in/abhisek-chaudhuri/}{Abhisek Chaudhuri}}
\end{center}
\vspace{-4.5mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-7mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:ac1959@cse.jgec.ac.in}{ac1959@cse.jgec.ac.in}  ~\textbullet~ Final Year, Computer Science \& Engineering ~\textbullet~ \(+91\) 7699646573
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.Tech in Computer Science \& Engineering, Final Year} \hfill 2015 - 2019 \\
\href{http://jgec.ac.in/}{Jalpaiguri Government Engineering College, West Bengal, India} \\
\hspace*{0.6em}\textbullet~ Current GPA - \textbf{9.07}/10 ~\textbullet~ Overall GPA - \textbf{8.55}/10 (May 2018)
%\begin{itemize}
 %\item Overall GPA - \textbf{8.55}/10 (Dec 2017)
%\end{itemize}
\\
\\
\textbf{High School} - \href{http://sainikschoolpurulia.com/}{Sainik School, Purulia} (CBSE) - 80.6\% \hfill 2012 - 2014 \\
\textbf{Secondary School} - \href{http://sainikschoolpurulia.com/}{Sainik School, Purulia} (CBSE) - 91.2\% \hfill 2007 - 2012
 
%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Experience}
\textbf{Summer Student, \href{http://www.iiserpune.ac.in/}{Indian Institute of Science Education and Research, Pune}} \hfill{Jun - July, 2018}\\
Successfully developed a module to optimize structure of a given molecule for an existing in-house drug design software. Developed the corresponding data structures and algorithms for the same.\\
\textbf{Libraries Used:} ~\textbullet~ Boost Graph Library ~\textbullet~ Eigen Matrix Library\\
\\
\textbf{Web Development Intern, \href{http://www.quicfind.com}{Quicfind, Aldinov Technologies, Kolkata}} \hfill Sep - Nov, 2017\\
Worked with the web designing team to implement the front-end of the end-consumer website. Concentrated on cross-platform compatibility of the UI with mobile-first approach.\\
\textbf{Keywords:} ~\textbullet~ Bootstrap 3 ~\textbullet~ HTML5 ~\textbullet~ PHP ~\textbullet~ jQuery ~\textbullet~ AJAX ~\textbullet~ Git\\
\\
\textbf{Web Development Intern, \href{http://www.tenpitech.com/}{TenPi Technologies Pvt. Ltd., Kolkata}} \hfill May - July, 2017\\
Designed and implemented UI design of the new company website, along with the back-end and developed the database schema for the same. Also worked on the back-end development of a vehicle logistics portal.
\textbf{Keywords:} ~\textbullet~ HTML5 ~\textbullet~ CSS3 ~\textbullet~ jQuery ~\textbullet~ MySQL ~\textbullet~ AWS

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Projects}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
\item
\textbf{Multi-server Authentication Using Biometrics} \textit{(ongoing)}:\\ Working on developing an efficient \& secure multi-server authentication framework using biometric verification as my Final Year B. Tech project.
\item
\textbf{\href{http://sristi.tech}{Sristi.Tech, website of the Techno-Management Fest of Jalpaiguri Govt. Engg. College}} :\\ Full-stack development of website for the annual techno-management fest of our college in the year 2018.
%\item \textbf{\href{https://gallery.cortanaintelligence.com/Experiment/Prediction-of-Housing-Prices-1}{Predicting Housing Prices Using Regression - Microsoft Azure Machine Learning Studio}} :\\
%A project developed by using linear regression to predict housing prices. Used Microsoft Azure Machine Learning Studio to train and deploy model.
 
\end{itemize}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Strongest Areas} - Full Stack Web Development, Algorithms\\
\textbf{Languages} - C++, Python, C, Java, HTML, CSS, PHP, JavaScript\\
\textbf{Tools/Frameworks} - Bootstrap, jQuery, STL, MySQL, Boost C++, Eigen, \LaTeX, Git\\
\textbf{Operating System} - GNU/Linux, Windows

%----------------------------------------------------------------------------------------
%	RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
%\section{Relevant \hspace{2mm} Courses}
%Data Structures and Algorithms, Operating System, Automata Theory, Discrete Mathematics, Object Oriented Programming, Computer Organization \& Architecture, Software Engineering, Unix Programming, Computer Graphics, Computer Networks, Databases, Advanced Java, Data Warehousing \& Data Mining, Compiler Design*, Web Technologies*, Image Processing*, Cloud Computing* \hfill
%\textit{(*ongoing)}


%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}
\begin{itemize}[leftmargin=*]
	\item
	Ranked in \textbf{top 4\% worldwide} in the \textbf{\href{https://www.codechef.com/JULY17}{July Long Challenge}} of CodeChef.
	\item
	Cleared the qualifier rounds \textbf{\href{https://www.facebook.com/hackercup/}{Facebook - HackerCup}} and \textbf{\href{https://codejam.withgoogle.com/codejam/}{Google CodeJam}}.
	\item
	Ranked consistently in \textbf{top 50} in various coding competitions organised by different colleges in India. 
	\item
	Ranked \textbf{under 1000} in \textbf{\href{https://tcscodevita.com}{TCS CodeVita}} pre-qualifier rounds of 2016 \& 2018.
	%\item
	%Ranked \textbf{8th out of 1206 participants} in \textbf{\href{https://www.hackerearth.com/challenge/college/code-hunt-tryst/leaderboard/}{Code Hunt - Tryst}}, organised by IIT Delhi.
	%\item
	%Ranked \textbf{9th out of 137 teams} in \textbf{\href{https://www.hackerrank.com/contests/h42-prelims-srijan17/leaderboard}{H42 Prelims, 2017, Srijan'17}} as a part of team \emph{codejarvis} organised by Jadavpur University.
	%\item
	%Ranked \textbf{8th out of 110 participants} and \textbf{44th out of 1308 participants} in \textbf{Code Chronicles \href{https://www.hackerearth.com/challenge/college/cc1/leaderboard/}{Season 1} \& \href{https://www.hackerearth.com/challenge/college/cc2/leaderboard/}{Season 2}} respectively, organised by Jalpaiguri Govt. Engg. College.
	
	
\end{itemize}

\section{Voluntary Services \& Positions of Responsibility}
\begin{itemize}[leftmargin=*]
	\item
	CodeChef Campus Representative of campus chapter \textbf{\href{https://www.codechef.com/campus_chapter/JGEC_Chef}{JGEC\_Chef}}.
	\item
	Lecturer at Coders' Club of our college.
	\item
	Volunteered as a student mentor of Junior Undergrad students to guide them for projects in the domains of \textbf{Web Development} \& \textbf{Python scripting}.
	%\item
	%Served as \textbf{House Captain} during the senior-most year of my schooling.
\end{itemize}

\section{Activities}
\begin{itemize}[leftmargin=*]
	\item
	Successfully completed \textbf{\href{https://goo.gl/NxdY6T}{C}, \href{https://goo.gl/mLoMF3}{Python}, \href{https://goo.gl/rQg0Dz}{GIMP}} and \textbf{\href{https://goo.gl/i67WIz}{LibreOffice Suite - Math}} training conducted by Spoken Tutorials, IIT Bombay.
	\item
	Active participation in online competitive coding platforms, \textbf{\href{https://www.hackerearth.com/@abhisek17}{HackerEarth}, \href{https://www.codechef.com/users/abhisek_ch}{CodeChef}} and \textbf{\href{http://www.spoj.com/users/abhisekssp4025/}{SPOJ}}.
	\item
	Algorithmic problem setting in \textbf{\href{https://hackerearth.com}{HackerEarth}}.
	\item
	Member of the problem setting team of coding competitions held in \textbf{Sristi}, techfest of our college.
\end{itemize}

%----------------------------------------------------------------------------------------
%	HOBBIES SECTION
%----------------------------------------------------------------------------------------
\section{Hobbies}
Coding and watching TV-series
\end{resume}
\end{document}